X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on a conventional source

### 2014-03-04 hedpc.tex
added intro to discussion

\section*{Results}
We introduce a method for phase contrast imaging which works on
conventional X-ray sources, covers the entire diagnostic X-ray energy range
and is compatible with compact imaging arrangements. The approach is based
on Talbot-Lau interferometry~\cite{Pfeiffer2006} and employs an edge-on
illumination approach for the grating design and arrangement. Our solution
removes one of the major hurdles which prevented grating interferometry from
being
applied at high energies so far, namely the fabrication of
gratings with high aspect ratios. The aspect ratio, given by
\begin{equation}
    \text{R} = \frac{2h}{p},
\end{equation}
where $p$ is the
grating period and $h$ the  structure height, is limited by the
fabrication process, usually photolithography~\cite{David2002} or X-ray
lithography~\cite{Mohr2012} since grating structures tend to collapse or deform
(e.g.\ due to capillary forces) if the aspect ratio is too high. For a given
setup length these parameters depend on the target energy $E$ according to
$p \propto 1/\sqrt{E}$ and $h \propto E^3$, and therefore $\textnormal{R}
\propto E^{7/2}$~\cite{Momose2003a}. If at $E=\SI{25}{\kilo\electronvolt}$
an aspect ratio for the absorption grating around $\textnormal{R}=30$ is
sufficient, it would
have to be at least $\num{128}$ for $E=\SI{100}{\kilo\electronvolt}$. This
is the case for the synchrotron interferometer with a design energy
of~\SI{82}{\kilo\eV}~\cite{Willner2013}, where an aspect ratio of \num{21}
is reported with a transmission of \SI{20}{\percent}. The aspect ratio in
the present experiment reaches \num{143}. Moreover,
when using a broad spectrum, photons above the design energy should also be
efficiently blocked by the gratings, thus requiring even higher aspect
ratios. The largest aspect ratios achieved by current fabrication
techniques~\cite{David2007,Kenntner2010} are around 60.

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Fig.~\ref{Fig:grating_mask}. Multiple gratings can reside on a
silicon chip with their specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy~\cite{David2002}. Using
gold as the phase shifting material, a structure length of
$h_1 = \SI{19.8}{\micro \metre}$ is required. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter~\cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$
it can absorb more than \SI{70}{\percent} of the incoming X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. The beam splitter and analyzer grating are
separated at the first fractional Talbot order~\cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources~\cite{Pfeiffer2006}. It is also made of gold structures
with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure}[h!]
    \centering
    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach and \ac{SEM}
        image of the grating. The top part of the 4 inch wafer shows
        five grating chips. From top to bottom, one source grating, two
        phase gratings and two analyzer gratings. The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. 
        The \ac{SEM} image shows the gold structures and the interrupting bridges
        that prevent the lamellae from collapsing~\cite{Kenntner2010}.}\label{Fig:grating_mask}
\end{figure}

Due to the large spectral acceptance~\cite{Weitkamp2005,Thuering2013c} of the
interferometer ($\SI{50}{\kilo\electronvolt}$ to
more than $\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
the source and analyzer gratings ($>90\%$ up to
$\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
the maximum of $\SI{160}{\kilo\volt}$. With a structure height of
approximately $\SI{100}{\micro \metre}$, the field of view in the vertical
direction is limited to one detector pixel row. In the horizontal direction,
the field of view is only limited by the grating size to
$\SI{30}{\milli\metre}$, but wider gratings can be fabricated with the same
method and the available technology on larger wafers. In addition to the standard components (source,
camera, interferometer), two optical slits, one in front of the source
grating, the other in front of the camera, were required for the collimation
of the beam in the vertical direction.

\section*{Discussion}
Several resistors and an integrated circuit are located on different layers
on the electronic chip in fig.~\ref{Fig:img_chip}. The radiographs were
acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
calculating the derivative along the horizontal axis. In the attenuation
image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. The reduced contrast of the 
soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper
layer, resulting in lower absorption contrast. Due to the weaker energy
dependence of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase contrast in
high-energy X-ray imaging, which may be useful to identify flaws in multilayered
structures such as electronic chips.
\begin{figure}[h!]
    \centering
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}\label{Fig:img_chip}
\end{figure}

@@

>>>>

\section*{Results}
We introduce a method for phase contrast imaging which works on
conventional X-ray sources, covers the entire diagnostic X-ray energy range
and is compatible with compact imaging arrangements. The approach is based
on Talbot-Lau interferometry~\cite{Pfeiffer2006} and employs an edge-on
illumination approach for the grating design and arrangement. Our solution
removes one of the major hurdles which prevented grating interferometry from
being
applied at high energies so far, namely the fabrication of
gratings with high aspect ratios. The aspect ratio, given by
\begin{equation}
    \text{R} = \frac{2h}{p},
\end{equation}
where $p$ is the
grating period and $h$ the  structure height, is limited by the
fabrication process, usually photolithography~\cite{David2002} or X-ray
lithography~\cite{Mohr2012} since grating structures tend to collapse or deform
(e.g.\ due to capillary forces) if the aspect ratio is too high.
Moreover, when using a broad spectrum, photons above the design energy
should also be efficiently blocked by the gratings, thus requiring even
higher aspect ratios. The largest aspect ratios achieved by current
fabrication techniques~\cite{David2007,Kenntner2010} are around 60.
For a given setup length these parameters depend on the target energy $E$
according to $p \propto 1/\sqrt{E}$ and $h \propto E^3$, and therefore
$\textnormal{R} \propto E^{7/2}$~\cite{Momose2003a}. If at
$E=\SI{25}{\kilo\electronvolt}$ an aspect ratio for the absorption grating
around $\textnormal{R}=30$ is sufficient, it would have to be at least
$\num{128}$ for $E=\SI{100}{\kilo\electronvolt}$. With our design, we reach
an aspect ratio of \num{143}, satisfying the above condition with a
transmission of less than \SI{1}{\percent} at \SI{100}{\kilo\eV}. As a
comparison, a recent interferometer implemented at a third generation
synchrotron facility~\cite{Willner2013} reported an aspect ratio of
\num{21} with a transmission as large as \SI{20}{\percent}
at~\SI{82}{\kilo\eV}.

@@

Grating design and fabrication is nonstandard and involves a complex mask
design, as shown in Fig.~\ref{Fig:grating_mask}. Multiple gratings can reside on a
silicon chip with their specific structure length and curvature. For the
current experiments, a symmetric interferometer with a grating period of $p
= \SI{2.8}{\micro\metre}$ for all gratings has been used. The design energy
is $\SI{100}{\kilo\electronvolt}$ and the beam splitter grating periodically
shifts the phase by zero and $\pi$ at this energy~\cite{David2002}. Using
gold as the phase shifting material, a structure length of
$h_1 = \SI{19.8}{\micro \metre}$ is required. The analyzer grating is an absorption mask
for sensing slight changes of the interference pattern generated by the beam
splitter~\cite{Momose2003a}. With a structure length of $h_2 =
\SI{800}{\micro \metre}$
it can absorb more than \SI{90}{\percent} of the incoming X-rays up to energies of 
$\SI{160}{\kilo\electronvolt}$. The beam splitter and analyzer grating are
separated at the first fractional Talbot order~\cite{Weitkamp2005},
resulting in an intergrating distance of $\SI{158}{\milli\metre}$. The
source grating splits the relatively large focal spot ($\sim
\SI{1}{\milli\metre}$) into an array of individually coherent, but mutually
incoherent sources~\cite{Pfeiffer2006}. It is also made of gold structures
with a length of $h_0 = h_2 = \SI{800}{\micro \metre}$.
\begin{figure}[h!]
    \centering
    \includegraphics[width=.6\textwidth]{figures/grating_mask.eps}
    \caption{Grating design mask for
        the edge-on illumination approach and \ac{SEM}
        image of the grating. The top part of the 4 inch wafer shows
        five grating chips. From top to bottom, one source grating, two
        phase gratings and two analyzer gratings. The
        gratings have different curvatures which are specific to the grating
        interferometer geometry. 
        The \ac{SEM} image shows the gold structures and the interrupting bridges
        that prevent the lamellae from collapsing~\cite{Kenntner2010}.}\label{Fig:grating_mask}
\end{figure}

Due to the large spectral acceptance~\cite{Weitkamp2005,Thuering2013c} of the
interferometer ($\SI{50}{\kilo\electronvolt}$ to
more than $\SI{160}{\kilo\electronvolt}$) and the high attenuation efficiencies of
the source and analyzer gratings (more than $90\%$ up to
$\SI{160}{\kilo\electronvolt}$), the voltage of the X-ray source was set to
the maximum of $\SI{160}{\kilo\volt}$. With a structure height of
approximately $\SI{100}{\micro \metre}$, the field of view in the vertical
direction is limited to one detector pixel row. In the horizontal direction,
the field of view is only limited by the grating size to
$\SI{30}{\milli\metre}$, but wider gratings can be fabricated with the same
method and the available technology on larger wafers. In addition to the standard components (source,
camera, interferometer), two optical slits, one in front of the source
grating, the other in front of the camera, were required for the collimation
of the beam in the vertical direction.

\section*{Discussion}
This work develops Talbot-Lau interferometry to a regime of
high photon energies.
High energies are required for the operation of computed
tomography and security scanners, in order to
penetrate materials with large thicknesses or high atomic number.

Additionally, the dose delivered to the patients could be reduced through
phase sensitivity at high energies: the dose depends mainly on the
absorption and it decreases with the third power of the photon energy~\cite{Momose2005}. On
the other hand, the phase interaction is only inversely proportional to the
energy and is therefore relatively much more relevant than absorption as the
energy increases, possibly leading to a decreased exposure for an equivalent
image quality.

We show the first images on a conventional laboratory source in this energy
range. In fig.~\ref{Fig:img_chip}, several resistors and an integrated
circuit are located on different layers on an electronic chip. The
radiographs were acquired in scanning mode, using a step size of
$\SI{100}{\micro \metre}$ along the $y$ axis. For a better comparison of the
magnified phase and attenuation images, the attenuation image has been
replaced with the differential attenuation image, which was obtained by
calculating the derivative along the horizontal axis. In the attenuation
image, the contrast of the soldering points of
the integrated circuit is reduced underneath the resistors, while in
the phase image, they can clearly be identified. The reduced contrast of the 
soldering points in the absorption image is due to beam hardening. The spectrum
impinging on these soldering point is hardened by the resistors in the upper
layer, resulting in lower absorption contrast. Due to the weaker energy
dependence of phase shifts ($1/E$ compared to $1/E^3$), phase-contrast images
are less sensitive to beam hardening~\cite{Chabior2011a}, which explains the
lower contrast reduction of the soldering points underneath the resistors in the
phase image of the chip. This result shows the benefit of the phase contrast in
high-energy X-ray imaging, which may be useful to identify flaws in multilayered
structures such as electronic chips.
\begin{figure}[h!]
    \centering
    \includegraphics[width=.5\textwidth]{figures/img_chip_dabs.eps}
    \caption{Radiographic scan of an electronic chip. The image was acquired
        with 24 phase steps per line and an exposure time of \SI{15}{\second} per
    step. The top right image shows the differential absorption image.}\label{Fig:img_chip}
\end{figure}

@@

\bibitem{Momose2005}
\bibinfo{author}{Momose, A.}
\newblock \bibinfo{title}{{Recent Advances in X-ray Phase Imaging}}.
\newblock \emph{\bibinfo{journal}{Japanese Journal of Applied Physics}}
  \textbf{\bibinfo{volume}{44}}, \bibinfo{pages}{6355--6367}
  (\bibinfo{year}{2005}).
